---
title       : Storm Explorer - Final Project for the course 'Developing Data Products'
subtitle    : Slidify Presentation
author      : ianf2015
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## What is Storm Explorer

1. Based on NOAA database of severe weather events between 1950 and 2011
2. Intend to show which events cause most human casualty and economic damage in different states
3. Created with R's Shiny package

--- .class #id 

## How to use

1. go to [storm explorer app](https://ianf2015.shinyapps.io/shiny-app/) 
2. select from pull-down menu the abbreviation of the state you want to explore
3. two bar charts will be shown with the top one showing the casualty figure from weather events and the bottom one showing econmic damage in thousands of US dollars

--- .class #id

## List of event types

```{r,echo=FALSE}
library(data.table)
library(reshape2)
mydata<-fread("data/stormevent.csv")
unique(mydata$Event_Type)
```

--- .class #id

## Example: State of New York

```{r,echo=FALSE}
tmp<-subset(mydata,State=="NY")
suppressWarnings(melted <- melt(tmp, id.vars=c("V1", "Event_Type","State")))
sumdata<-dcast(melted,Event_Type~variable,sum)
barplot(sumdata$Casualty,names.arg=sumdata$Event_Type,cex.names=0.4,horiz=TRUE,las=1,col="red",main="Casualty Figure From Severe Weather Types",xlab="Number of Casualty")
```
